---
title: "ANOVA"
author: "Amira Ibrahim"
date: "October 16, 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
#Attach Data 
```{r DietWeightLoss, echo=TRUE}
Diet_Data <- read.table(file.choose() , header = T , sep = "\t")
attach(Diet_Data)
```

##check normality 
```{r , echo=TRUE}
library(moments)
skewness(WeightLoss)
```
accepted level from -1 to +1
```{r , echo=TRUE}
kurtosis(WeightLoss)
```
accepted level from -2 to +2 may to +3
```{r , echo=TRUE}
boxplot(WeightLoss~Diet , main = "Relation between type of diet & weight loss")
```
visually it is normally distributed
```{r , echo=TRUE}
shapiro.test(WeightLoss)
```
p-value > 0.05 , Fail to reject H0 , Data is normally distributed

##Analysis of relation between type of diet and weight lose : 
#comparing one categorical variable(Diet) contain more than 2 levels and one numerical variable :
#using one way ANOVA 
#H0 : Mean weight lose is the same for all types of diet
```{r , echo=TRUE}
ANOVA1 <- aov(formula = WeightLoss~Diet , data=Diet_Data)
summary(ANOVA1)
```
p-value < 0.05 , reject H0

#I need to Know which type of Diet is significant :
```{r , echo=TRUE}
TukeyHSD(ANOVA1)
plot(TukeyHSD(ANOVA1), las=1)
```
Diffrence in mean between C-A , C-B is significant 
Diffrence in mean C-B is more significant than C-A

```{r, include=FALSE}
library(tinytex)
options(tinytex.verbose = TRUE)
```